%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{apps:intro}
 
This chapter aims to overview existing techniques for building ZKP-based applications, including designing the protocols to meet best-practice security requirements.
We distinguish between high-level and low-level applications, where the former are the protocols designed for specific use-cases and the latter are the necessary underlying operations or sub-protocols.
Each use case admits a circuit, and we discuss the sub-circuits needed to ensure security and functionality of the protocol.
We refer to the circuits as \emph{predicates} and the sub-circuits as \emph{gadgets}:

\begin{itemize}
    \item {\bfseries \hypertarget{def:predicate}{Predicate}:} 
    The relation or condition that the statement and witness must satisfy.
    Can be represented as a circuit.

    \item \textbf{\hypertarget{def:gadget}{Gadget}:} 
    The underlying tools needed to construct the predicate.  
    In some cases, a gadget can be interpreted as a security requirement (e.g., using the commitment verification gadget is equivalent to ensuring the privacy of underlying data).
\end{itemize}

Recall from \refsec{security:syntax} the syntax of a proof system between a prover and verifier.
As we will see, the protocols can be abstracted and generalized to admit several use-cases; 
similarly, there exist compilers that will generate the necessary gadgets from commonly used programming languages. 
Creating the constraint systems is a fundamental part of the applications of ZKP, which is the reason why there is a large variety of front-end software options available.


\paragraph{Functionality vs.\ performance}\pslabel{par:apps:intro:functionality-vs-performance}
The design of ZKPs is subject to the tradeoff between functionality and performance. 
Users would like to have powerful ZKPs, in the sense that the system permits constructing proofs for any predicate, which leads to the necessity of universal ZKPs. 
On the other hand, users would like to have efficient constructions. 
According to Table~\ref{tab:apps:APIS-and-interfaces-by-univ-and-preproc}, it is possible to classify ZKPs as:
(i) universal or non-universal;
(ii) scalable or non-scalable; and 
(iii) preprocessing or non-preprocessing. 

Item (i) is related to the functionality of the underlying ZKP, while items (ii) and (iii) are related to performance. 
The utilization of zk-SNARKs allows universal ZKPs with very efficient verifiers. 
However, many proposals depend upon an expensive preprocessing, which makes such systems hard to scale for some use-cases. 
A technique called \emph{Proof-Carrying Data} (PCD), originally proposed in Ref.~\cite{2010:ICS:proof-carrying-data}, allows obtaining \emph{recursive composition} for existing ZKPs in a modular way.
This means that zk-SNARKs can be used as a building block to construct scalable and non-preprocessing solutions. 
The result is not only an efficient verifier, as in zk-SNARKs, but also a prover whose consumption of computational resources is efficient, in particular with respect to memory requirements, as described in Refs.~\cite{2014:crypto:Scalable-ZK-via-Cycles-of-EC} and~\cite{2013:Recursive-Composition-and-Bootstrapping-for-SNARKS-and-Proof-carrying-Data}.
\loosen


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Organization}
\refsec{apps:scope-use-cases} mentions different types of verifiability properties of interest to applications.
\refsec{apps:previous-works} enumerates some prior works.
\refsec{apps:gadgets-within-predicates} describes possible gadgets useful for diverse applications.
The subsequent three sections present three ZKP use-cases:
\refsec{apps:id-framework} describes a use-case related to \emph{identity management};
\refsec{apps:asset-transfer} examines an application context related to \emph{asset transfer};
\refsec{apps:regulation-compliance} exemplifies one use-case related to \emph{regulation compliance}.
