\presection{Executive summary}
\label{sec:prelim:executive-summary}


Zero-knowledge proofs (ZKPs) are an important privacy-enhancing tool from cryptography. 
They allow proving the veracity of a statement, related to confidential data, without revealing any information beyond the validity of the statement.
ZKPs were initially developed by the academic community in the 1980s, and have seen tremendous improvements since then.
They have since become feasible in practice for application in multiple domains of interest to the industry, and to a large community of developers and researchers. 
ZKPs can have a positive impact in industries, agencies, and for personal use, by allowing privacy-preserving applications where designated private data can be made useful to third parties, despite not being disclosed to them.


The development of this reference document aims to serve the broader community, particularly those interested in understanding ZKP systems, making an impact in their advancement, and using related products.
This is a step towards enabling wider adoption of ZKP technology, which may precede the establishment of future standards.
However, this document is not a substitution for research papers, technical books, or standards. 
It is intended to serve as a reference handbook of introductory concepts, basic techniques, implementation suggestions and application use-cases. 


ZKP systems involve at least two parties: a prover and a verifier.  
The goal of the prover is to convince the verifier that a \emph{statement} is true, without revealing any additional information.  
For example, suppose the prover holds a birthdate certificate digitally signed by an authority.
In order to access some service, the prover may have to prove being at least 18 years old, that is, that the prover \emph{knows} a certificate, tied to their identify and digitally signed by a trusted certification authority, stating a birthdate consistent with the age claim.
A ZKP allows this, without the prover having to reveal the birthdate.


\xetexfontscale{.985}{
This document describes important aspects of the current state of the art in ZKP
\hyperref[chap:security]{security}, 
\hyperref[chap:paradigms]{paradigms}, 
\hyperref[chap:implem]{implementation}, and 
\hyperref[chap:apps]{applications}.
There are several use-cases and applications where ZKPs can add value.
To better assess this it is useful to benchmark implementations under several metrics, evaluate tradeoffs between security and efficiency, and develop an interoperability basis.
The security of a proof system is paramount for the system users, but efficiency is also essential for user experience.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ABOUT CHAPTER "SECURITY"
\label{par:exec-summ:chap-security}
The ``\hyperref[chap:security]{Security}'' chapter introduces the baseline terminology and security concepts of ZKP systems.
A ZKP system can be described with three components: {\tt setup}, {\tt prove}, {\tt verify}. 
The {\tt setup} determines the initial state of the prover and the verifier, including private and common elements, such as private and public keys, or a common reference string.
The {\tt prove} and {\tt verify} components are the prover and verifier's algorithms, respectively, possibly interactive.
Overall they need to ensure three main security requirements: completeness, soundness, and zero-knowledge.

\xetexfontscale{.99}{
Completeness requires that if both {\tt prove} and {\tt verify} are correct, and if the statement is true, then at the end of the interaction the verifier is convinced of this fact.
Soundness requires that not even a malicious prover can convince the verifier of a false statement.
Zero knowledge requires that even a malicious verifier cannot extract from the proof process any information beyond the truthfulness of the given statement.
Other properties and variations may be built in by design, as desired features, such as succinctness, non-interactivity, transferability and composability, among others.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ABOUT CHAPTER "PARADIGMS"
\pslabel{par:exec-summ:chap-paradigms}
The ``\hyperref[chap:paradigms]{Paradigms}'' chapter presents an overview of paradigms for constructing zero-knowledge proofs for general statements, namely those related to non-deterministic polynomial (NP) relations.
The presentation describes a modern perspective of composition of an \emph{information theoretic} (IT) system, based on ideal components, a \emph{cryptographic compiler} (CC), where cryptographic elements come into play, and an \emph{arithmetization} system to encode the actual public data (statement and instance) and private data (witness) that determine the specific proof taking place.
The provided organization allows for a systematized covering/characterization of many modern ZKP systems, many of which enable succinct proofs.
Future updates to this chapter should include additional examples for specialized languages/relations, which can follow  a different approach.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ABOUT CHAPTER "IMPLEMENTATION"
\pslabel{par:exec-summ:chap-implementation}
The ``\hyperref[chap:implem]{Implementation}'' chapter focuses on devising a framework for the implementation of ZKPs, which is important for interoperability.
One important aspect to consider upfront is the representation of statements.
In a ZKP protocol, the statement needs to be converted into a mathematical object.
For example, in the case of proving that an age is at least 18, the statement is equivalent to proving that the private birthdate {\texttt Y$_1$-M$_1$-D$_1$} (year-month-day) satisfies a relation with the present date {\texttt Y$_2$-M$_2$-D$_2$}, namely that their distance is greater than or equal to 18 years.
This simple example can be represented as a disjunction of conditions: 
    {\tt Y$_2>$Y$_1$+18}, 
    or {\tt Y$_2$=Y$_1$+18}~$\wedge$~{\tt M$_2$}$>${\tt M$_1$},
    or {\tt Y$_2$=Y$_1$+18 }$\wedge${ \tt M$_2$=M$_1$ }$\wedge${ \tt D$_2$}$\geq${\tt D$_1$}.
An actual conversion suitable for ZKPs, namely for more complex statements, can pose an implementation challenge. 
There are nonetheless various techniques that enable converting a statement into a mathematical object, such as a circuit.
This document gives special attention to representations based on a Rank-1 constraint system (R1CS) and quadratic arithmetic programs (QAP), which are adopted by several ZKP solutions in use today.
Also, the document gives special emphasis to implementations of non-interactive proof systems.
\loosen


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ABOUT CHAPTER "APPLICATIONS"
\pslabel{par:exec-summ:chap-applications}
The privacy enhancement offered by ZKPs can be applied to a wide range of scenarios.  
The ``\hyperref[chap:apps]{Applications}'' chapter presents three use-cases that can benefit from ZKP systems: identity framework; asset transfer; regulation compliance. 
In a privacy-preserving identity framework, one can for example prove useful personal attributes, such as age and state of residency, without revealing more detailed personal data such as birthdate and address.
In an asset-transfer setting, financial institutions that facilitate transactions usually require knowing the identities of the sender and receiver, and the asset type and amount. 
ZKP systems enable a privacy-preserving variant where the transaction is performed between anonymous parties, while at the same time ensuring they and their assets satisfy regulatory requirements.
In a regulation compliance setting, ZKPs enables an auditor to obtain proof that a process satisfies a number of requirements, without having to learn details about how they were achieved.
These use cases, as well as a wide range of many other conceivable privacy-preserving applications, can be enabled by a common set of tools, or gadgets, for example including commitments, signatures, encryption and circuits.
\loosen


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% CONCLUDING PARAGRAPH
\xetexfontscale{.995}{\pslabel{par:exec-summ:conclude}
The development of secure, practical, and interoperable ZKP applications requires a balanced interplay between security concepts and implementation guidelines.
Solutions provided by ZKP technology must be ensured by careful security practices and realistic assumptions.
This document aims to summarize security properties and implementation techniques that help achieve these goals.
}