\chapter{Version history}
\label{app:version-history}

The ZKProof Community Reference (ZkpComRef) development follows a sequence of main versions:
\loosen

\begin{itemize}\setlength{\itemsep}{.75em}

\item \textbf{Version 0 [\dateVersionZero]: Baseline documents.}
The proceedings of the 1st ZKProof Workshop (May 2018), with contributions settled by 2018-08-01 and available at \href{https://zkproof.org/documents}{ZKProof.org}, along with the \hyperref[sec:prelim:charter]{ZKProof Charter}, constitute the starting point of the ZKProof Community reference.
Each of the three Workshop tracks --- security, applications, implementation --- led to a corresponding proceedings document, titled ``ZKProof Standards \emphbrkt{track name} Track Proceedings''.
The ZKProof charter is also part of the baseline documents.


\item \textbf{Version 0.1 [\dateVersionZeroDotOne]: LaTeX/PDF compilation.}
The several proceedings composing version 0 were ported to LaTeX code and compiled into a single PDF document entitled ``ZKProof Community Reference'' (version 0.1) for presentation and discussion at the 2nd ZKProof workshop. 
That version included editorial adjustments for easier indexation and consistent style. 


\item \textbf{Version 0.2 [\dateVersionZeroDotTwo]: Consolidated draft.}
The process of consolidating the draft community reference document started at the 2nd ZKProof workshop (April 2019), where an editorial process was introduced and several ``breakout sessions'' were held for discussion on focused topics, including the ``NIST comments on the initial ZKProof documentation''.
The discussions yielded suggestions of topics to develop and incorporate in a new version of the document.
Several concrete items of ``proposed contributions'' were then defined as GitHub issues.
Subsequently, various submitted contributions provided content improvements, such as:
	distinguish \hyperref[security:zkp-knowledge-vs-membership]{ZKPs of knowledge vs.\ of membership};
	recommend \hyperref[security:Efficiency]{security parameters for benchmarks};
	clarify some \hyperref[security:terminology]{terminology} related to ZKP systems (e.g., statements, CRS, R1CS);
	discuss \hyperref[paradigms:interactivity]{interactivity vs.\ non-interactivity, and transferability vs.\ deniability};
	clarify the scope of use-cases and applications; 
	update the \hyperref[tab:list-gadgets]{``gadgets'' table}; add new \hyperref[references]{references}.
The new version also includes numerous editorial improvements towards a consolidated document, namely a substantially reformulated frontmatter with several new sections (\hyperref[sec:prelim:abstract]{abstract}, \hyperref[sec:prelim:about-this-version]{about this community reference}, \hyperref[app:version-history]{change log}, \hyperref[app:acknowledgments]{acknowledgments}, \hyperref[sec:prelim:IP]{intellectual property}, \hyperref[sec:prelim:executive-summary]{executive summary}), a reorganized structure with a new chapter (still to be completed) on construction \hyperref[chap:paradigms]{paradigms}.
The changes are tracked in a ``diff'' version of the document.


\item \textbf{Version 0.3 [\dateVersionZeroDotThree]: Paradigms addon.}
The main update was in the \nameref{chap:paradigms} chapter, replacing the old ``Taxonomy of Constructions'' section by three new sections: \refsecnamenum{paradigms:background}, \refsecnamenum{paradigms:IT} and \refsecnamenum{paradigms:CC}.
New placeholder sections (contributions needed) were also included for \refsecnamenum{paradigms:specialized} and \refsecnamenum{paradigms:proof-composition}.
Other small changes include an improvement of \reftab{tab:example-scenarios-zkps} in \refsec{security:terminology}, a new paragraph in the \hyperref[]{executive summary}.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Additional documentation covering the development history of the ZkpComRef can be found in the 
ZKProof GitHub repository (\myurl{https://github.com/zkpstandard/zkreference})
and the ZKProof webpage (\sloppy\mbox{\myurl{https://docs.zkproof.org/reference}})
and forum (\myurl{https://community.zkproof.org}).
\loosen