\def\tmpSecTitle{ZKProof charter}
\phantomsection\section*{\addcontentsline{toc}{section}{\tmpSecTitle}\centering \tmpSecTitle}
\label{sec:prelim:charter}

\vspace{2.5em}\hfill{\bfseries Boston, May 10th and 11th 2018}

\vspace{3em}
The goal of the ZKProof Standardardization effort is to advance the use of Zero Knowledge
Proof technology by bringing together experts from industry and academia. To further the goals
of the effort, we set the following guiding principles:

\begin{itemize}
\item The initiative is aimed at producing documents that are open for all and free to use.
	\begin{itemize}[label={$\circ$}]
	\item As an open initiative, all content issued from the ZKProof Standards Workshop is
				under Creative Commons Attribution 4.0 International license.\luis{Consider adding a logo and mention "CC BY 4.0 International License" in the cover page. The statement mentions workshop in singular. Could this be widened to cover edits performed in the documents made available by ZKProof for communitary collaboration?}
	\end{itemize}

\item We seek to represent all aspects of the technology, research and community in an
inclusive manner.
\item Our goal is to reach consensus where possible, and to properly represent conflicting
views where consensus was not reached.
\item As an open initiative, we wish to communicate our results to the industry, the media
and to the general public, with a goal of making all voices in the event heard.
	\begin{itemize}[label={$\circ$}]
	\item Participants in the event might be photographed or filmed.
	\item We encourage you to tweet, blog and share with the hashtag \#ZKProof. Our official twitter handle is @ZKProof.
	\end{itemize}
\end{itemize}

For further information, please refer to \myemail{contact@zkproof.org}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\def\tmpSecTitle{ZKProof code of conduct}
\phantomsection\section*{\addcontentsline{toc}{section}{\tmpSecTitle}\centering \tmpSecTitle}
\label{sec:prelim:code}

\vspace{2.5em}\hfill{\bfseries Boston, May 10th and 11th 2018}

\vspace{3em}
All participants, speakers and sponsors of the ZKProof Standard Workshop shall adhere to the
following code of conduct to ensure a safe and productive environment for everybody\footnote{This code of conduct is adapted from that of TEDx.\luis{Consider adding a link. Is it the code of conduct from TEDx or TED?}}:


\textbf{At the workshop, you agree to:}
\begin{itemize}
\item Respect the boundaries of other attendees.
\item Respect the opinions of other attendees even if you are not in agreement with them.
\item Avoid aggressively pushing your own services, products or causes.
\item Respect confidentiality requests by participants.
\item Look out for one another.
\end{itemize}

\textbf{These behaviors don't belong at the workshop:}
\begin{itemize}
\item Invasion of privacy
\item Being disruptive, drinking excessively, stalking, following or threatening anyone.
\item Abuse of power (including abuses related to position, wealth, race or gender).
\item Homophobia, racism or behavior that discriminates against a group or class of people.
\item Sexual harassment of any kind, including unwelcome sexual attention and inappropriate physical contact.
\end{itemize}

For further information, please refer to \myemail{contact@zkproof.org}

